Evaluating the Effects of Tracker Reliability and Field of View on a Target Following Task in Augmented Reality

### 2009-06-25 trunk/Paper/paper.tex
Added paragraph about component of immersion

>>>>

We are considering FOV and the sensor dropouts, or \emph{presence of the augmented imagery}, as the varying components of immersion in our study.  This is based off of Slater's definition \cite{slater} of immersion as the ``objective level of fidelity of the sensory stimuli produced by a technological system,''  enabling us to view the components of immersion as controllable aspect of the technological system.
